\thetitle

### 2020-11-21 writing/results.tex
Small changes to sec 7

There are
three immediate take-aways from the figure. First, the effort for successfully
debugging interesting scenarios (in green) for the random mode of the
rational programmer follows  a normal distribution, as expected.\footnote{The
random mode distribution is indistinguishable for all three semantics and thus the figure~\ref{fig:effort-table} 
only shows one plot.} In contrast, in the other modes, successful effort coalesces at
the left side of the plot, meaning that in most cases the programmer needs
to type a single component to debug a scenario. Even in the minority of
cases where a blame or exception mode has to work harder, the number of
modules that that need to be typed is small relative to the random mode.

@@

In Transient, similar to Natural,
most failures are due to unhelpful exception information (1851 for both
Transient first and last blame).  
However, Transient also has a substantial
number of failures because scenarios hit the time and memory
limits of our experiment (~ 770 scenarios).  Additionally, there are nearly a 1000 cases where
Transient reports an empty blame set which leaves the rational programmer
without hints about how to proceed.
In~\ref{sec:threat:transient}, we discuss how both of these causes of
failure for transient affect our experiment.

>>>>

There are
three immediate take-aways from the figure. First, the effort for successfully
debugging interesting scenarios (in green) for the random mode of the
rational programmer follows  a normal distribution, as expected.\footnote{The
random mode distribution is indistinguishable for all three semantics and thus the figure~\ref{fig:effort-table} 
only shows one plot.} In contrast, in the other modes, successful effort coalesces at
the left side of the plot, meaning that in most cases the programmer needs
to type a single component to debug a scenario.

@@

In Transient, similar to Natural,
most failures are due to unhelpful exception information (1851 for both
Transient first and last blame).  
However, Transient also has a substantial
number of failures because scenarios hit the time and memory
limits of our experiment (~ 770 scenarios).  Additionally, there are nearly a 1000 cases where
Transient reports an empty blame set which leaves the rational programmer
without hints about how to proceed.
In~\ref{sec:threat:transient}, we discuss how both of these causes of
failure for Transient affect our experiment.
